Approximation as Differentiation: Notes

### 2025-07-05 main/first-order.tex
Tweak.

\begin{proposition}
\label{prop:biproducts:from-product-or-coproduct}
In any $\CMon$-category:
\begin{enumerate}
\item If $Z$ is a product of $X$ and $Y$ then it is also coproduct of $X$ and $Y$, with injections given by
$\inj_1 = \prodM{\id}{0}$ and $\inj_2 = \prodM{0}{\id}$.
\item If $Z$ is a coproduct of $X$ and $Y$, then it is also a product of $X$ and $Y$, with projections given by $\pi_1 =
\coprodM{\id}{0}$ and $\pi_2 = \coprodM{0}{\id}$.
\item $X$ is terminal iff it is initial.
\end{enumerate}
\end{proposition}

>>>>

\begin{proposition}
\label{prop:biproducts:from-product-or-coproduct}
In any $\CMon$-category:
\begin{enumerate}
\item Any product of $X$ and $Y$ is also coproduct of $X$ and $Y$, with injections given by $\inj_1 =
\prodM{\id}{0}$ and $\inj_2 = \prodM{0}{\id}$.
\item Any coproduct of $X$ and $Y$  is also a product of $X$ and $Y$, with projections given by $\pi_1 =
\coprodM{\id}{0}$ and $\pi_2 = \coprodM{0}{\id}$.
\item $X$ is terminal iff it is initial.
\end{enumerate}
\end{proposition}
